### 2014-02-01 thesis/src/chapters/chapter-design.tex
Thesis: container analysis

\subsubsection{Analysis}

\subsubsection{Planning}
During planning phase, procedure to enact desired state in resource is created. Depending on problem it may involve only one step on a complex workflow. Before implementing planning module, following issues should be taken into consideration:
\begin{asparaenum}
 \item[\textbf{Priorities}] One of key benefits of a containerisation is multi-tenancy. However, as a consequence, containers contends again each other to get access to resources. This issue can be mitigated by one of the following: \begin{inparaenum}[1)]
    \item avoid overprovisioning, each tenant has guaranteed resource pool
    \item prioritise tenant, each tenant has assigned priority that indicates its business value; that priority is used to favour one tenant at the expense of the others.
 \end{inparaenum}

@@

\subsubsection{Execution}
Execution module role is simple yet it plays a role that cannot be underestimated: carrying procedure scheduled beforehand during planning. To do so, it leverages effectors and API exposed by a container. In case of a self-learning system, change plan and its effects should be recorded to serve as a reference point in future.

\subsubsection{Knowledge}

>>>>

\subsubsection{Analysis}
The analysis module processes data received from monitoring component. It aims to evaluate it against various models and possibly determine if container require further intervention. The analyse function can employ variety of models, performing complex simulations or predictions. As \cite{LiWoZh05} proposes, it analysis can be based on:
\begin{itemize}
 \item Queue-based Performance Models
 \item Dynamic models
 \item Monotonic static models
 \item Policy based models
\end{itemize}
Self-learning container manager should also use a predictive approach \cite{JiPeLiCh11} and track changes made in a container \cite{ZhYaWo05}.

Cloud-SAP requires to at least support policy-based model such as one threshold-model \cite{tong1978threshold}.

\subsubsection{Planning}
During planning phase, procedure to enact desired state of a container is created. Depending on problem it may involve only one step such as increasing CPU or a more complex one like container migration. Before implementing planning module, following issues should be taken into consideration:
\begin{asparaenum}
 \item[\textbf{Priorities}] One of key benefits of a containerisation is multi-tenancy. However, as a consequence, containers contends again each other to get access to resources. This issue can be mitigated by one of the following: \begin{inparaenum}[1)]
    \item avoid overprovisioning, each tenant has guaranteed resource pool
    \item prioritise tenant, each tenant has assigned priority that indicates its business value; that priority is used to favour one tenant at the expense of the others.
 \end{inparaenum}

@@

\subsubsection{Execution}
Execution module role is simple yet it plays a role that cannot be underestimated: carrying procedure scheduled beforehand during planning. To do so, it leverages effectors and API exposed by a container. Collectively, these actions scales container vertically, for example:
\begin{itemize}
 \item increase / decrease CPU
 \item increase / decrease memory
 \item increase / decrease disk space
 \item increase / decrease network bandwidth
\end{itemize}
Not every hypervisor supports dynamic vertical scaling, some requires a container to be restared. Noticeably, lightweight containers are flexible in th

In case of a self-learning system, change plan and its effects should be recorded to serve as a reference point in future.
